Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-03 demystify.tex
Updates from Overleaf

\paragraph{Not getting interviews} While it is generally good to get interview, not getting an interview does not mean you're out.  Many programs do not have the tradition of interviewing applicants. For example, at GMU, most of our admitted students with TA do not go through any interviews.

@@

Faculty often receive many "cold" e-mails from prospective students. Most of the time, we ignore these emails, but in some rare occasions we do answer them. So how to write an email that get our attention?

@@

So what to do if you want someone to look at your profile and give input? You could ask your professors, collaborators, or those who have previously applied. For these kind of feedback,  don't ask strangers like random profs., instead ask someone you have personal connection with.

@@

\section{Why did I get rejected?}
Many possible reasons!  Other than having weak profile (e.g., research potentials, GPA, LoRs, SOP), here are some that you might not expect:
\begin{itemize}
  \item  \emph{Your English scores (e.g., IELTS or TOEFL) are not high enough}.  While professors might not care much about these, there is a certain minimum set by the college or the university that you need to pass to get admitted, especially for TA funding (e.g., you need to be able to communicate well with students as a TA).  Moreover, while professors are willing to fight to get you admitted, they might be reluctant to go against the standard requirement of the university or college on English scores.  Note this is mostly for international students, as domestic one do not have to take these tests.

>>>>

\paragraph{Not getting interviews} While it is generally good to get interview, not getting an interview does not mean you're out.  Many programs do not have the tradition of interviewing applicants. For example, at GMU, most of our admitted students with TA do not go through interviews.

@@

Faculty often receive "cold" e-mails from prospective students. Most of the time, we ignore these emails, but in some rare occasions we do answer them. So how to write an email that get our attention?

@@

So how to get someone to look at your profile and give input? You could ask your professors, LoR writers, collaborators, or those who have previously applied. For these kind of feedback, ask someone you have personal connection with.

@@

\section{Why did I get rejected?}
Many possible reasons!  Other than not having a strong profile (e.g., research potentials, GPA, LoRs, SOP), here are some that you might not expect:
\begin{itemize}
  \item  \emph{Your English scores (e.g., IELTS or TOEFL) are not high enough}.  While professors might not care much about these, there is a certain minimum set by the college or the university that you need to pass to get admitted, especially for TA funding (e.g., you need to be able to communicate well with students as a TA).  Moreover, while professors are willing to fight to get you admitted, they might be reluctant to go against the standard requirement of the university or college on English scores.  Note this is mostly for international students, as domestic one do not have to take these tests.
